A Fredholm operator approach to the plate buckling problem

### 2018-07-12 doc/draft-01/08append.tex
Updating appendix A

\section{Proof of the invertibility of the Farkas representation}
\label{sec:farkproof}

>>>>

\section{Proof of the invertibility of the Farkas representation}
In this appendix, we prove~\cref{lem:farkinv} which is restated here
as~\cref{lem:farkinv_app}.

In the following lemma, we present an integral indentity involving the
Green's function of the Helmholtz-biharmonic equation.
\begin{lem}
Suppose that $\Gbh$ is the Green's function of the Helmholtz-biharmonic equation 
with Helmholtz parameter $k$. Suppose that $v:\R^{2} \to \R$ is a compactly supported smooth
function. Then
\begin{equation}
\int_{\R^{2}} \Gbh(\xx,\yy) \Delta (\Delta + k^2) v(\yy) d\yy = v(\xx)
\end{equation}
\end{lem}
\begin{proof}
Suppose that $r>0$. 
Let $B_{r}(\xx)$ denote the ball of radius $r$ centered at the origin
and let $\partial B_{r}(\xx)$ denote its boundary.
Then applying Green's second identity twice, we get 
\begin{align}
\int_{\R^{2} \setminus B_{r}(\xx)} \Gbh(\xx,\yy) \Delta (\Delta +k^{2}) v(\yy)
&=
\int_{\R^{2} \setminus B_{r}(\xx)} \Delta \Gbh (\xx,\yy) (\Delta + k^2) 
v(\yy) + \\
& \hspace{5ex}\int_{\partial B_{r}(\xx)} \Gbh(\xx,\yy) (\Delta + k^{2})
\frac{\partial}{\partial n}v(\yy) \, dS - \\
& \hspace{5ex}\int_{\partial B_{r}(\xx)} \frac{\partial }{\partial n} \Gbh(\xx,\yy) 
(\Delta + k^2) v \, dS \\
&= \int_{\R^{2} \setminus B_{r}(\xx)} \Delta (\Delta + k^2)G(\xx,\yy) v(\yy)
d\yy  - \nonumber \\
& \hspace{5ex}\int_{\partial B_{r}(\xx)} (\Delta + k^2) 
\frac{\partial }{\partial n} \Gbh(\xx,\yy) v \, dS + \nonumber\\
& \hspace{5ex}\int_{\partial B_{r}(\xx)} (\Delta + k^2) 
\Gbh(\xx,\yy) \frac{\partial}{\partial n}v \, dS - \nonumber \\
& \hspace{5ex}\int_{\partial B_{r}(\xx)}  
\frac{\partial }{\partial n} \Gbh(\xx,\yy) \Delta v\, dS + \\
& \hspace{5ex}
\int_{\partial B_{r}(\xx)} \Gbh(\xx,\yy) \Delta \frac{\partial v}{\partial n}
\, dS \nonumber
\end{align}
For all $\yy \in \partial B_{r}(x)$, there exists a constant $C$ such that
$\Gbh$ satisfies the following equations
\begin{align}
(\Delta + k^2) \frac{\partial }{\partial n} G(\xx,\yy) &= 
-\frac{1}{2\pi r} \label{eq:estapp1}\\
\left|(\Delta + k^2) G(\xx,\yy) \right| &\leq C \log{(r)} \label{eq:estapp2}\\
\left|\frac{\partial }{\partial n} G(\xx,\yy) \right| &\leq C r\log{(r)} 
\label{eq:estapp3}\\
\left| G(\xx,\yy) \right| &\leq C r^{2} \log{(r)} \label{eq:estapp4}\, .
\end{align}
Furthermore, $\Gbh$ satisfies $\Delta (\Delta + k^2) \Gbh(\xx,\yy) = 0$
for all $\yy \in \R^{2} \setminus B_{r}(\xx)$.
Using the estimates in~\cref{eq:estapp1,eq:estapp2,eq:estapp3,eq:estapp4}, 
and the smoothness of $v$, we get
\begin{equation}
\int_{\R^{2} \setminus B_{r}(\xx)} \Gbh(\xx,\yy) \Delta (\Delta + k^2) v(\yy) 
d \yy = \frac{1}{2\pi r} \int_{\partial B_{r}(\xx)} v(\yy) dS + 
O(r \log(r)) \, \label{eq:estapp5}.
\end{equation}
The result then follows by taking the limit $r\to 0$ in~\cref{eq:estapp5}. 
\end{proof}
\label{sec:farkproof}
